This is the title [Article v\versionnumber]

### 2022-08-28 manuscript/manuscript.tex
Move the info on running GIST into its own section.

\section{Running GIST}
\todo{We could put the examples for how to run GIST, how to visualize a dx file, how to create more dx files, etc., here and move them out. The actual tutorial could be only the streptavidin/biotin thing, and could be shortened a lot if we move the example inputs here.}

\subsection{Running the GIST analysis}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}

>>>>

\section{Running GIST}
%\subsection{Running the GIST analysis}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}
